\documentclass[defaultstyle,11pt]{thesis}

\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage{lscape}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{mathtools}

\usepackage{xspace}
\newcommand{\ttbar}{$\textrm{t}\bar{\textrm{t}}$\xspace}
\newcommand{\bbbar}{$\textrm{b}\bar{\textrm{b}}$\xspace}
\newcommand{\ptmiss}{$p_{T}^{\mathrm{miss}}$\xspace}
\newcommand{\pt}{$p_{T}$\xspace}

\title{Search for supersymmetry using boosted Higgs bosons and missing transverse momentum in proton-proton collisions at 13 TeV}

\author{Frank}{Jensen}
\otherdegrees{M.S., University of Colorado Boulder, 2014\\B.A., University of California Berkeley, 2008}
\degree{Doctor of Philosophy} {Ph.D., experimental high-energy physics}
	
\dept{Department of}	{Physics}
\advisor{Professor}{Kevin Stenson}
\reader{Professor William Ford}
%\readerThree{Professor James Nagle}
%\readerFour{Professor Markus Pflaum}
%\readerFive{Professor Senarath de Alwis}

\abstract{ \OnePageChapter
A search for physics beyond the Standard Model in events with one or more high-momentum Higgs bosons decaying to pairs of b quarks in association with missing transverse momentum is presented. The data, corresponding to an integrated luminosity of $\mathrm{35.9}\,\mathrm{fb}^{-1}$, were collected with the CMS detector at the Large Hadron Collider in proton-proton collisions at the center-of-mass energy $\sqrt{s}\,=\,13\,\mathrm{TeV}$. The analysis utilizes a new b quark tagging technique based on jet substructure to identify jets from $\mathrm{Higgs}\,\rightarrow\,b\bar{b}$ decays. Events are categorized by the number of $b\bar{b}$-tagged jets, the mass of the jets, and the missing transverse momentum. No significant deviations from Standard Model expectations are observed. In the context of supersymmetry, limits on the cross sections of pair-produced gluinos are set, assuming that gluinos decay to quark pairs and a Higgs or Z boson, and the lightest supersymmetric particle. The decay chain proceeds through an intermediate particle assumed to be the second lightest in the theory. Assuming a large mass splitting between these two neutral particles, and 100$\%$ NLSP branching fraction to Higgs bosons, the lower limit on the gluino mass is found to be 2010 GeV.
}

\dedication[Dedications]{
\textit{The taxpayers.}
} 

\begin{document}

\input introduction.tex
\input sm.tex
\input mssm.tex
\input lhc.tex
\input detector.tex
\input eventreco.tex
\input analysis.tex
\input conclusions.tex

\bibliographystyle{ieeetr}
\bibliography{thesis}

\appendix
\input bb.tex
\input reinterpretation.tex
\input bbsf.tex

\end{document}
